---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQsPEvBKbuqYGGlAs8vcq3PikMOvTA2YStG3lrxiwO8IeUbI0TTM-wqtWhTgZtOIKvJOd3fC7kE3EpP/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    ad_length = 2,
    device = 3,
    video_category = 4,
    ad_category = 5,
    interest = 6,
    relatedness = 7
  ) %>%
  filter(
    !is.na(ad_length),
    !is.na(ad_category),
    !is.na(interest),
    !is.na(relatedness)
  )


num_responses <- latest_data$ad_length %>% length()

mean_ad_length <- latest_data$ad_length %>%
  mean(na.rm = TRUE) %>% round(1)

min_ad_length <- latest_data$ad_length %>% min(na.rm = TRUE)

max_ad_length <- latest_data$ad_length %>% max(na.rm = TRUE)
```

```{css}
body {font-family: Arial, sans-serif;
  padding: 20px;}

h2 {color: #1f4e79;}

```

## Are YouTube ads actually relevant?

This dynamic report analyses responses collected from a Google Form about YouTube in-video ads.

The data looks at ad length, the device used to watch YouTube, and the category of the video being watched.

The number of responses collected so far is `r num_responses`.

The mean ad length is `r mean_ad_length` seconds.

The shortest ad length recorded is `r min_ad_length` seconds.

The longest ad length recorded is `r max_ad_length` seconds.

```{r}
#Were users interested in the ads?

latest_data %>%
   ggplot() +
  geom_bar(aes(x = interest)) +
  labs(title = "Interest in ads",
    x = "Interest",
    y = "Count")
```

```{r}

#How related were the ads to the videos?
latest_data %>%
  ggplot() +
  geom_bar(aes(x = relatedness)) +
  labs(title = "Ad relatedness to video", x = "Relatedness", y = "Count")
```

```{r}
#What types of ads are being shown?
latest_data %>%
  ggplot() +
  geom_bar(aes(x = ad_category)) +
  labs( title = "Ad categories", x = "Ad category",  y = "Count")

